Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-05-07 paper/PaperCEUS/PaperCEUS_rev1.Rmd
Mention jittering subpoints in the limitations, close #48

## Model replicability and limitations

This paper focus primarily on the potential of making cycling and PT a viable alternative to car trips, and the socio-environmental benefits of such a shift.

This analysis can be applied to other metropolitan areas, providing a basis for decision-making and policy development to support a modal shift from car to PT.
This process involves a minimum of data requirements, such as the origin-destination data, road network, and the PT GTFS data, which are available in most metropolitan areas.
Furthermore, it is essential to incorporate existing cycling level targets specific to those areas or consider the possibility of utilising the same targets as outlined in the Portuguese national strategy, in order to compare results with different areas.

@@

A strength of the approach is that there is no requirement for sensitive individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations in terms of being able to identify exactly which trips are being replaced -- in terms of the age of people making the trips, the types of car they drive, and other individual or vehicle level variables.
We assumed uniformity in the type of vehicle for all replaced car journeys, albeit with variations in the fuels utilized.
Additionally, we assumed consistency in the health impacts across all individuals for the replaced car trips
This approach is a simplification of the real-world scenario, but it is a necessary one to make the analysis feasible and reproducible.

A further refinement could be to differentiate between ‘simpler’ no-transfer PT trips (which require less person effort) and more arduous multi-transfer PT trips, using the same methods, by relaxing the assumption of no-transfers between PT modes in `r5r`.
This would led to a larger number of total daily trips that can be made by cycling + PT, in particular in locations where the PT network is less complex and requires more transfers.
We could also set a different maximum lenght of cycling stage, extending the bicycle catchment area.
However, despite the added value of a sensibility analyses, they would also increase the overall complexity, and would have an impact on the explainability of the results to be used by policy makers.

>>>>

## Generalizability and limitations

This paper focus primarily on the potential for replacing trips currently made by car with combined cycling and public transport trips, and the associated social and environmental benefits.
While the results are specific to the Lisbon Metropolitan Area, the approach is designed to be generalizable to other metropolitan areas.

An important aspect of the approach from a generalizability perspective is that it has specific data requirements, including origin-destination, road network, and the GTFS data.
Such datasets are available to transport planners in many areas.
In areas where such datasets do not exist, the value of research such as this could provide a motivation to collect and open-up transport data.
For this study we have used Portugal's national cycling targets as the basis of the scenarios; the approach can be adapted to other targets, or to other policy goals, such as reducing congestion or improving air quality.

@@

A strength of the approach is that there is no requirement for sensitive individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations.
The approach cannot show exactly which trips are being replaced, in terms of the age of people making the trips, the types of car they drive, and other individual or vehicle level variables.
We assumed uniformity in the type of vehicle for all replaced car journeys, albeit with variations in the fuels utilized.
Additionally, we assumed consistency in the health impacts across all individuals for the replaced car trips.
This approach is a simplification of reality to enable the analysis of a large region on available computing resources.
Future work could seek to increase the resolution of the results, and move towards a more individual-level analysis, for example by using agent and activity-based models using tools such as MATSim.
This direction of travel would require substantial resources outside the scope of this study; another way to improve the spatial resolution of results would be to use higher resolution 'subpoints' as the basis of the desire line 'jittering' process.
We would also like to explore the potential for probabilistic routing to improve the spatial resolution of the results.

A further refinement could be to differentiate between 'simpler' no-transfer PT trips (which require less person effort) and more arduous multi-transfer PT trips, using the same methods, by relaxing the assumption of no-transfers between PT modes in the routing engine.
This would led to a larger number of total daily trips that can be made by cycling + PT, in particular in locations where the PT network is less complex and requires more transfers.
We could also set a different maximum lenght of cycling stage, extending the bicycle catchment area.
However, despite the added value of a sensibility analyses, they would also increase the overall complexity, and would have an impact on the explainability of the results to be used by policy makers.
